`make.events`

### 2023-02-21 inst/gitbook/05_other_functionalities.Rmd
done for bd.params

>>>>

If you are a visual person and your `bd.params` objects are getting a bit too complicated to remember, you can always quickly plot them (the function will sample from the `bd.params` object and show the results):

```{r}
par(mfrow = c(2,2))
plot(make.bd.params(), main = "Default birth-death parameters")
plot(make.bd.params(speciation = runif,
               speciation.args = list(min = 0.5, max = 1.5)),
     main = "Uniform speciation between 0.5 and 1.5\n(no extinction)")
plot(make.bd.params(speciation = runif,
                    speciation.args = list(min = 0.5, max = 1.5)),
     main = "Uniform speciation between 0.5 and 1.5\n(no extinction)")
plot(make.bd.params(speciation = runif, extinction = runif, joint = TRUE),
     main = "Joint uniform speciation and extinction")
plot(make.bd.params(speciation = rnorm, extinction = runif,
                    joint = FALSE, abs = FALSE),
     main = "Disjoint normal speciation and uniform extinction")
```
